---
title: "p8105_hw1_ra2965"
output: github_document
---

# Problem 1

##Create a data frame and try to get the means

Create a data frame comprised of 5 vectors in 5 different data types, and try to take the means of each vector in this data frame:

```{r}

library(tidyverse)

hw1_df = tibble(
  vec_numeric = rnorm(8),
  vec_logical = vec_numeric > 0,
  vec_char = c('a','b','c','d','e','f','g','h'),
  vec_factor = factor(c("low", "medium", "high", "low","medium","high","low","medium"))
)
  
mean(pull(hw1_df, vec_numeric))

mean(pull(hw1_df, vec_logical))

mean(pull(hw1_df, vec_char))

mean(pull(hw1_df, vec_factor))
```

I tried to take the mean of each variable in my dataframe. Numeric vector and logical vector works, while character vector and factor vector don't work. 

Since the vector types of the variable "vec_char"" and "vec_factor"" are not numeric or logical, there is a warning and it returns NA.

##Try to convert the vectors' type:


```{r}
convert_log_num = as.numeric(pull(hw1_df, vec_logical))
product_num_random = convert_log_num*pull(hw1_df, vec_numeric)

convert_log_fac = as.factor(pull(hw1_df, vec_logical))
product_fac_random = convert_log_fac*pull(hw1_df, vec_numeric)
 
convert_fac_num = as.numeric(convert_log_fac)
produc_num_num = convert_fac_num*pull(hw1_df, vec_numeric)

```
‘*’ is not meaningful for factors so I cannot get the product of factor vector and the random sample.


#Problem 2

##Create a new data frame:


```{r}

set.seed(1)
plot_df = tibble(
  x = rnorm(500),
  y = rnorm(500),
  var_logical = c(x + y > 1),
  var_num = as.numeric(var_logical),
  var_fac = as.factor(var_logical))

       
```

In this data frame, there are `r nrow(plot_df)` rows and `r ncol(plot_df)` colums. 

The mean of x is `r mean(pull(plot_df,x))`, the median of x is `r median(pull(plot_df,x))` and the standard deviation of x is `r sd(pull(plot_df,x))`. 

The proportion of cases for which x + y > 1 is `r mean(pull(plot_df,x) + pull(plot_df,y) > 1)`.

##Scatterplots of y vs x:

In the three plots, color points used three different types of variable: logical, muneric, factor

```{r}

ggplot(plot_df, aes(x = x, y = y, color = (var_logical))) + geom_point()
ggsave("plot_logical.pdf")

ggplot(plot_df, aes(x = x, y = y, color = (var_num))) + geom_point()
       
ggplot(plot_df, aes(x = x, y = y, color = (var_fac))) + geom_point()

```
For the scatterplot in which color points using the logical variabl, the FALSE points are colored as red, and the TRUE points are colored as green.

For the scatterplot in which color points using the numeric variabl, the color scale is from dark blue to light blue corresponding to 0.00-1.00.

For the scatterplot in which color points using the factor variabl, the FALSE points are colored as red, and the TRUE points are colored as green.

